---
title: "Examples after update the sampling method"
date: 2019-08-28
output: pdf_document
---


# Example 1 


Suppose we simulate the data from the following joint distribution: 
$$f(s,t) = \frac{1}{1000} (s + t)$$
where $s \in (0,10)$ and $t \in (0,10)$.

Simulate data. 

#### The marginal plots is: 

```{R include = FALSE}
setwd('/Users/yaolanqiu/Desktop/NYU/Research/Survival/update-2019-08-27/example1000')
library(png)
library(knitr)
library(grid)
```

```{r fig.width=3, fig.height=3,echo=FALSE,  fig.align = "center"}
img <- readPNG("/Users/yaolanqiu/Desktop/NYU/Research/Survival/update-2019-08-27/example1000/1.png")
grid.raster(img)
```


#### The estimation plot:

```{r fig.width=3, fig.height=3,echo=FALSE,  fig.align = "center"}
img <- readPNG("/Users/yaolanqiu/Desktop/NYU/Research/Survival/update-2019-08-27/example1000/2.png")
grid.raster(img)
```

#### The mean abs difference 

```{R include = FALSE}
load('/Users/yaolanqiu/Desktop/NYU/Research/Survival/update-2019-08-27/example1000/example1000.RData')
load('/Users/yaolanqiu/Desktop/NYU/Research/Survival/update-2019-08-27/example1000/s_est.RData')
sture = result$sture
s_est = s_est
spt1 = result$spt1
spt2 = result$spt2
sr = result$sr
se = result$se

tables = c(mean(abs(sture - s_est)), # 0.02429018
mean(abs(sture - spt1)), # 0.0250697
mean(abs(sture - spt2)), # 0.02520928 
mean(abs(sture - sr)), # 0.0002958531
mean(abs(sture - se))) # 0.02294636

tables = round(tables, 3)
tables = matrix(tables, 1, 5)
colnames(tables) = c('KM','Slud1','Slud2','Riemann','Integral') 
```

```{R echo = FALSE}
kable(tables)
```

#### The distribution of true $\rho(t)$

```{R fig.width=3, fig.height=3,echo=FALSE,  fig.align = "center"}
hist(result$rho_value, main = 'Histogram of rho', xlab = 'rho')
```

# Example 2 Tsiatis

#### The functions 

|   Function |   Description | Expression|
|-------------:|------------------:|------------------------------------------------:|
|$P(T < t, C < c)$ |Joint CDF | $1 + exp(-\lambda t - \mu c -\theta tc) - exp(-\lambda t) -  exp(-\mu c)$| 
|$f(t, c)$ | Joint PDF|$(\lambda \mu - \theta + \lambda \theta t + \mu \theta c + \theta^2 t c) exp(-\lambda t - \mu c - \theta c t )$|
|$f_t(t)$  |Marginal PDF of T|$\lambda exp(-\lambda t)$|
|$S_t(t)$  |Survival function of T|$exp(-\lambda t)$ |
|$f_c(c)$  | Marginal PDF of C| $\mu exp(-\mu c)$ | 
|$S_c(c)$  | $P_c(C > c)$|$exp(-\mu c)$ | 
|$S_x(t)$  | $P(T > t, C > t)$|$exp(-\lambda t - \mu t -\theta t^2)$|
|$\psi(t)$ | $\int_{t}^{\infty} f(t,c) dc$ | $(\lambda + \theta t) exp(-\lambda t - \mu t - \theta t^2 )$|

**Parameter settings (consistent to Tsiatis's example):** 

* scenario 1:  $\lambda = 0.1, \mu = 0.2$,$\theta = 0.02$

* scenario 2:  $\lambda = 1, \mu = 1$, $\theta = 1$

P.S. the problem here is tha the inverse function cannot be calculated. Just estimated. 


#### The marginal plots is ($\lambda = 0.1, \mu = 0.2$,$\theta = 0.02$): 


```{r fig.width=3, fig.height=3,echo=FALSE,  fig.align = "center"}
setwd('/Users/yaolanqiu/Desktop/NYU/Research/Survival/update-2019-08-27/tsiatis')
img <- readPNG("1.png")
grid.raster(img)
```


#### The estimation plot:

```{r fig.width=3, fig.height=3,echo=FALSE,  fig.align = "center"}
setwd('/Users/yaolanqiu/Desktop/NYU/Research/Survival/update-2019-08-27/tsiatis')
img <- readPNG("2.png")
grid.raster(img)
```

#### The mean abs difference 

```{R include = FALSE}
setwd('/Users/yaolanqiu/Desktop/NYU/Research/Survival/update-2019-08-27/tsiatis')
load('result.RData')
load('s_est1.RData')
sture = result$sture
s_est = s_est
spt1 = result$spt1
spt2 = result$spt2
sr = result$sr
se = result$se

tables = c(mean(abs(sture - s_est)), # 0.02429018
mean(abs(sture - spt1)), # 0.0250697
mean(abs(sture - spt2)), # 0.02520928 
mean(abs(sture - sr)), # 0.0002958531
mean(abs(sture - se))) # 0.02294636

tables = round(tables, 3)
tables = matrix(tables, 1, 5)
colnames(tables) = c('KM','Slud1','Slud2','Riemann','Integral') 
```

```{R echo = FALSE}
kable(tables)
```

#### The distribution of true $\rho(t)$

```{R fig.width=3, fig.height=3,echo=FALSE,  fig.align = "center"}
hist(result$rho_value, main = 'Histogram of rho', xlab = 'rho')
```



#### The marginal plots is ($\lambda = 1, \mu = 1$, $\theta = 1$): 


```{r fig.width=3, fig.height=3,echo=FALSE,  fig.align = "center"}
setwd('/Users/yaolanqiu/Desktop/NYU/Research/Survival/update-2019-08-27/tsiatis')
img <- readPNG("3.png")
grid.raster(img)
```


#### The estimation plot:

```{r fig.width=3, fig.height=3,echo=FALSE,  fig.align = "center"}
setwd('/Users/yaolanqiu/Desktop/NYU/Research/Survival/update-2019-08-27/tsiatis')
img <- readPNG("4.png")
grid.raster(img)
```

#### The mean abs difference 

```{R include = FALSE}
setwd('/Users/yaolanqiu/Desktop/NYU/Research/Survival/update-2019-08-27/tsiatis')
load('result2.RData')
load('s_est2.RData')
sture = result$sture
s_est = s_est
spt1 = result$spt1
spt2 = result$spt2
sr = result$sr
se = result$se

tables = c(mean(abs(sture - s_est)), # 0.02429018
mean(abs(sture - spt1)), # 0.0250697
mean(abs(sture - spt2)), # 0.02520928 
mean(abs(sture - sr)), # 0.0002958531
mean(abs(sture - se))) # 0.02294636

tables = round(tables, 3)
tables = matrix(tables, 1, 5)
colnames(tables) = c('KM','Slud1','Slud2','Riemann','Integral') 
```

```{R echo = FALSE}
kable(tables)
```


#### The distribution of true $\rho(t)$

```{R fig.width=3, fig.height=3,echo=FALSE,  fig.align = "center"}
hist(result$rho_value, main = 'Histogram of rho', xlab = 'rho')
```
