---
title: "How rho will affect the value of $S_{km}, S_{p1}, S_{p2}$"
date: 2019-07-31
output: pdf_document
---

To generate examples with the $\rho_i$ value we want, we may use the piecewise example in Slud's paper, whose joint distribution is: 
$$ f(t,s)=\left\{
\begin{aligned}
& f_1(t) f_C(s) & & \text{ } (t \leq s)\\
& f_C(s) \frac{S_1(s)}{S_2(s)} f_2(t) &  & \text{ } (t > s)
\end{aligned}
\right.$$

Let 

* $f_1(t) = exp(-t)$, $S_1(s) = exp(-x)$

* $f_C(s) = exp(-s)$, $S_C(s) = exp(-s)$

* $f_2(t) = \rho exp(-\rho t)$ , $S_2(s) = exp(- \rho t)$

* $\rho(t) = \frac{h_2(t)}{h_1(t)} = \rho$, which is a constant. 

Then 
$$ f(t,s)=\left\{
\begin{aligned}
& exp(-t - s) & & \text{ } (t \leq s)\\
& \rho exp( - \rho t + (\rho - 2)s)&  & \text{ } (t > s)
\end{aligned}
\right.$$
And 
$$f(t) = \frac{2 \rho - 2}{\rho - 2} exp(-2t) - \frac{\rho}{\rho - 2} exp(-10t)$$
$$S(t) = \frac{2 \rho - 2}{2 \rho - 4}exp(-2t) - \frac{1}{\rho - 2} exp(-\rho t)$$
$$\psi(t) = exp(-2t), \text{ } S_x(t) = exp(-2t)$$

## Set $\rho$ values

Let's $\rho = 0, 0.1, 0.9, 1, 1.1, 1.01, 10, 100$ 

Simulate 200 paired data points from the associated joint distribution $f(t,s)$.

## The censor percentage

```{R include = FALSE}
library(survival)
library(png)
library(grid)
library(knitr)

setwd('/Users/yaolanqiu/Desktop/NYU/Research/Survival/rho and sp-2019-07-31')

mis_per = c(); mis_per_100 = c()
diff_km = c(); diff_km_100 = c()
diff_sp1 = c(); diff_sp1_100 = c()
diff_sp2 = c(); diff_sp2_100 = c()

# censoring percentage
rho_value = c(c(0, 0.1, 0.9, 1, 1.1, 1.01, 10, 100))
for(i in 1:8){
  
  RHO = rho_value[i]
  S = function(t){
    res = 0.5 * (2 * RHO - 2) / (RHO - 2) * exp(-2 * t) - 1 / (RHO - 2) * exp(- RHO * t)
    return(res)
  }
  
  names = paste('result-',RHO,'.RData', sep = '')
  load(names)
  data = result$data
  s1 = result$s1
  s2 = result$s2
  mis_per = c(mis_per, 1-sum(data$status)/dim(data)[1])
  
  # differences beween true 
  ## qian 100 ge de difference 
  fit_km = survfit(Surv(time, status) ~ 1, data=data)
  s_est = fit_km$surv
  t_est = fit_km$time
  S_est = data.frame(S_est = s_est, time = fit_km$time)
  diff_km = c(diff_km, mean(abs(s_est - S(t_est))))
  diff_sp1 = c(diff_sp1, mean(abs(s1 - S(data$time))))
  diff_sp2 = c(diff_sp2, mean(abs(s2 - S(data$time))))
  
  diff_km_100 = c(diff_km_100, mean(abs(s_est - S(t_est))[1:100]))
  diff_sp1_100 = c(diff_sp1_100, mean(abs(s1 - S(data$time))[1:100]))
  diff_sp2_100 = c(diff_sp2_100, mean(abs(s2 - S(data$time))[1:100]))
  
  # plots 
 }
```

```{R echo =FALSE}
aaa =  matrix(round(mis_per,3),1,8)
colnames(aaa) = rho_value
rownames(aaa) = c('Censor percent')
kable(aaa)
```

When $\rho$ is close to 0, there is less censoring. Otherwise, the censor percentage is around 50 $\%$.

## The differences between true values

Differences between all times points: 
```{R echo =FALSE}
bbb = rbind(round(diff_km,4), 
            round(diff_sp1,4), round(diff_sp2,4))
colnames(bbb) = rho_value
rownames(bbb) = c('KM','Sp1','Sp2')
kable(bbb)
```

Differences between the first 100 subjects' times points:
```{R echo =FALSE}
ccc = rbind( round(diff_km_100,4), 
            round(diff_sp1_100,4), round(diff_sp2_100,4))
colnames(ccc) = rho_value
rownames(ccc) = c('KM','Sp1','Sp2')
kable(ccc)
```

## The Plot
```{r fig.width=6, fig.height=6,echo=FALSE,  fig.align = "center"}
img <- readPNG("/Users/yaolanqiu/Desktop/NYU/Research/Survival/rho and sp-2019-07-31/try1.png")
 grid.raster(img)
```

```{r fig.width=6, fig.height=6,echo=FALSE,  fig.align = "center"}
img <- readPNG("/Users/yaolanqiu/Desktop/NYU/Research/Survival/rho and sp-2019-07-31/try2.png")
 grid.raster(img)
```



